---
output:
  html_document:
    toc: false
    theme: flatly
    highlight: zenburn
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=FALSE, tidy=TRUE, message=FALSE, warning=FALSE)
read_chunk("../../code/anomCalcAsScript.R")
```

##
##
## anomCalcAsScript.R

`anomCalcAsScript.R` is similar to `anomCalc.R` except that it is, under certain conditions, sourced later in `anomalies.R` in script form rather than as calling a function.
The result is that same as with `anomCalc.R`, which is the calculation of climate anomalies geotiffs.

The methods differ in that calling this script from `anomalies.R` rather than calling the `anomCalc` function, offers a different point of parallelization.
Instead of parallelizing across data sets, `anomCalcAsScript.R` is often used to process a single data set while parallelizing across twelve months.

This is ideal for CRU data sets, for reprocessing a single GCM, or for processing multiple GCMs one at a time where the GCMs may differ substantially in respective file sizes.
However, this is strictly available for CRU at this time, which is always processed one data set at a time (hence there is no reason not to use this method).
This option remains currently unavailable for GCM anomalies geotiff generation until some code updates can be made.

### R code

```{r anom_script}
```
