---
output:
  html_document:
    toc: false
    theme: spacelab
    highlight: zenburn
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=FALSE, tidy=TRUE, message=FALSE, warning=FALSE)
read_chunk("../../code/anomalies.R")
```

##
##
## anomalies.R

This script generates monthly climate anomalies geotiffs.
`anomalies.R` uses the original annual geotiffs and the climatologies previously generated from these originals by `climatologies.R`.
`climatologies.R` must be run before `anomalies.R` for any given data set.

This is done for each month and for the climate variables temperature and precipitation, and in some cases sea level pressure.
Each mutli-band geotiff contains annual bands, the number of bands depending on the number of years in the original data set.

After anomalies are created, they may be downscaled to alternate climatologies of higher spatial resolution, e.g., PRISM 771-m, PRISM 2-km, or CRU 2.0 10-minute.
Examples of downscaled data products include SNAP's CMIP3 and CMIP5 global climate models and CRU 3.0, 3.1, and 3.22.

### R code

```{r anom}
```
