---
output:
  html_document:
    toc: false
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=FALSE, tidy=TRUE, message=FALSE, warning=FALSE)
read_chunk("../../code/ds_world10min.R")
```


##
##
## ds_world10min.R

This script downscales monthly climate anomalies geotiffs to CRU 2.0 10-minute resolution monthly climatologies, which cover the world grid less some extreme latitudes.
The monthly climatologies used are technically derived climatologies which incorporate some methods that help make downscaling more robust to extreme outliers and downscaling artifacts.
For this reason they are not identical to the original CRU 2.0 10-minute monthly climatologies.

Unlike the `climatologies.R` and `amomalies.R` which create their respective geotiffs for any of a number of different data sets,
this downscaling script strictly performs downscaling to 10-minute resolution using CRU climatologies.
Furthermore, though similar, the methods used in this version of downscaling are not the same as those employed when downscaling to the higher-resolution PRISM climatologies for example.

`ds_world10min.R` is called with command line arguments by one of two SLURM scripts, `ds_world10min_cru.slurm` or `ds_world10min_gcm.slurm`.

### R code

#### Setup

```{r setup}
```

#### Processing function

```{r function}
```

#### Run downscaling

```{r run}
```
